Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-07-18 ms.tex
JKT comments on section 2.

\begin{deluxetable}{lrrrr}
\tablecaption{List of photometric observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Weather} &
\colhead{Airmass} &
\colhead{Seeing} &
\colhead{Amplitude, $A$} \\
\colhead{UT} & & & (\arcsec) & \\
 }
\startdata
2016 Jun 10 & Clouds	& \nodata & \nodata &  \nodata \\
2016 Jun 12 & Clear 	& 1.29 $\rightarrow$ 1.06 $\rightarrow$ 1.10	& 1.3 &	0.94 $\pm$ 0.16 \\
2016 Jun 14 & Clear 	& 1.47 $\rightarrow$ 1.06 $\rightarrow$ 1.12	& 1.4 &	0.70 $\pm$ 0.18\\
2016 Jul 12 & Clear 		& 1.19 $\rightarrow$ 1.06 $\rightarrow$ 1.63	& 1.2 &	0.78 $\pm$ 0.14 \\
2016 Jul 14 & Mostly clear	& 1.24 $\rightarrow$ 1.06 $\rightarrow$ 1.55 & 1.2 & 	1.33 $\pm$ 0.14 \\
2016 Jul 16 & Clear 		& 1.36 $\rightarrow$ 1.06 $\rightarrow$ 1.26	& 1.4 & 	2.14 $\pm$ 0.19 \\
\enddata
\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper telescope.
The seeing is expressed as the median FWHM for the night in arcseconds.}
\end{deluxetable}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
\caption{Reference-corrected time series photometry \shStar\ for all nights (blue circles).
Orange squares mark 20 minute flux bins.
The expected transit epochs from the \kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
We also show the average Short Cadence \kepler\ light curves for each of the transit events for comparison with the average.
Transits are clearly visible for all five nights except for UT2016-06-14.}\label{fig:allNightrefCorrect}
\end{centering}
\end{figure*}

To ease the visual comparison of the models and measured data, we bin the 61-inch Mont4K data into 20 minute long bins, shown in Figure \ref{fig:allNightrefCorrect}.
Obvious cosmic ray outliers were discarded by removing points with fluxes below 0.98 and above 1.02 times the median flux.
The error bars for the binned data are calculated from the standard error in the mean for each bin.
When calculating the best fit model and posterior distribution of parameter, however, the un-binned data is used.

@@

We examine the 17 total quarters of \kepler\ data to understand the statistics of the transits and put the 2013-2016 observations in context. Mainly, we sought to evaluate how likely/unlikely were the weak transits observed in 2013-2014 and normal transits in 2016.
We downloaded all 17 quarters of \kepler\ Long-Cadence data from the MAST archive beginning on 2009 May 13 and ending on 2013 April 08 for a total of 1425 days or 2181.5 orbits.
The \kepler\ data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 phase window.
All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
The secondary eclipses are used to quantify the noise in the transit depths.

>>>>

\begin{deluxetable}{lrrrr}
\tablecaption{List of photometric observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Weather} &
\colhead{Airmass} &
\colhead{Seeing} &
\colhead{Amplitude, $A$} \\
\colhead{UT} & & & (\arcsec) & \\
 }
\startdata
2016 Jun 10 & Cloudy	& \nodata & \nodata &  \nodata \\
2016 Jun 12 & Clear 	& 1.29 $\rightarrow$ 1.06 $\rightarrow$ 1.10	& 1.3 &	0.94 $\pm$ 0.16 \\
2016 Jun 14 & Clear 	& 1.47 $\rightarrow$ 1.06 $\rightarrow$ 1.12	& 1.4 &	0.70 $\pm$ 0.18\\
2016 Jul 12 & Clear 		& 1.19 $\rightarrow$ 1.06 $\rightarrow$ 1.63	& 1.2 &	0.78 $\pm$ 0.14 \\
2016 Jul 14 & Mostly clear	& 1.24 $\rightarrow$ 1.06 $\rightarrow$ 1.55 & 1.2 & 	1.33 $\pm$ 0.14 \\
2016 Jul 16 & Clear 		& 1.36 $\rightarrow$ 1.06 $\rightarrow$ 1.26	& 1.4 & 	2.14 $\pm$ 0.19 \\
\enddata
\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper telescope.
The seeing is expressed as the median FWHM for the night in arcseconds.}
\end{deluxetable}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/all_kic1255_phot/all_kic1255_refcor.pdf}
\caption{Reference-corrected time series photometry \shStar\ for all nights (blue circles).
Orange squares mark 20 minute flux bins for visual clarity.
The expected transit epochs from the \kepler-based ephemeris \citep{vanWerkhoven2014} are shown as vertical red bars.
We also fit each light curve with a model that scales the average \kepler\ short cadence data (Equation \ref{eq:transFitting}) shown in green.
Transits are clearly visible for all nights except for UT 2016 Jun 14.}\label{fig:allNightrefCorrect}
\end{centering}
\end{figure*}

To ease the visual comparison of the models and measured data, we bin the 61-inch Mont4K data into 20 minute long bins, shown in Figure \ref{fig:allNightrefCorrect}.
Obvious cosmic ray outliers were discarded by removing points (at any epoch within the reference-corrected time series) with fluxes below 0.98 and above 1.02 times the median flux for the night.
The error bars for the binned data are calculated from the standard error in the mean for each bin.
When calculating the best fit model and posterior distribution of parameter, however, the un-binned data is used.

@@

We examine the 17 total quarters of \kepler\ data to understand the statistics of the transits and put the 2013-2016 observations in context. Mainly, we sought to evaluate the likelihood of the weak transits observed in 2013-2014 and normal transits in 2016.
We downloaded all 17 quarters of \kepler\ Long-Cadence data from the MAST archive beginning on 2009 May 13 and ending on 2013 April 08 for a total of 1425 days or 2181.5 orbits.
The \kepler\ data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 phase window.
All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
The secondary eclipses are used to quantify the noise in the transit depths.
